Nested sampling with two objective functions

### 2015-11-22 Paper/ms.tex
Upper corner count

Our proposed algorithm (introduced in Section~\ref{sec:algorithm}) makes use
of a quantity we call the corner count. For any values $(\ell_1, \ell_2)$,
the prior mass for which both objective functions are lower is
\begin{eqnarray}
X(\ell_1, \ell_2) &=& \int \pi(L_1, L_2) \mathds{1}\left(L_1 < \ell_1, L_2 < \ell_2 \right)
 \, dL_1 \, dL_2
\end{eqnarray}
This is the two dimensional cumulative distribution function (CDF) of
$L_1$ and $L_2$. The corner count is a related quantity when we have
a collection of $N$ particles in the $L_1$-$L_2$ plane.
The corner count of particle $i$ is defined as the number of particles with
a lower value of {\em both} objective functions compared to particle $i$:
\begin{eqnarray}
C_i &=& \sum_{\substack{j=1\\{j \neq i}}}^N \mathds{1}\left(L_1(\xx_j) < L_1(\xx_i),
L_2(\xx_j) < L_2(\xx_i)
\right).\label{eqn:corner_count}
\end{eqnarray}
Graphically, on a plot of $L_2$ vs. $L_1$ the corner count is the number of
particles in the rectangle whose upper right corner is at
$\left(L_1(\xx_i), L_2(\xx_i)\right)$ (see Figure~\ref{fig:joint2} for an
example).

>>>>

Our proposed algorithm (introduced in Section~\ref{sec:algorithm}) makes use
of the (two dimensional) cumulative distribution of the objective functions.
For any values $(\ell_1, \ell_2)$ of the objective functions,
the prior mass for which both $L_1 > \ell_1$ {\em and} $L_2 > \ell_2$ is:
\begin{eqnarray}
X(\ell_1, \ell_2) &=& \int \pi(L_1, L_2)
\mathds{1}\left[L_1 > \ell_1, L_2 > \ell_2 \right]
 \, dL_1 \, dL_2
\end{eqnarray}
When the prior $\pi$ is approximated with a set of $N$
particles $\{\xx_i\}_{i=1}^N$
(Monte Carlo samples ``drawn from'' $\pi$),
$X(\ell_1, \ell_2)$ can be approximated by:
\begin{eqnarray}
\hat{X}(\ell_1, \ell_2) &=&
\frac{1}{N}
\sum_{i=1}^N \mathds{1}\left[L_1(\xx_i) > \ell_1,
L_2(\xx_i) > \ell_2\right].\label{eqn:corner_count}
\end{eqnarray}
Graphically, on a plot of $L_2$ vs. $L_1$, $\hat{X}(\ell_1, \ell_2)$
is the fraction of particles in the rectangle whose upper right corner is at
$\left(\ell_1, \ell_2\right)$ (see Figure~\ref{fig:joint2} for an
example).
